### 2020-08-25 thesis/thesis.tex
[thesis] More descriptive parts about cohandlers

    \subsection{Coinductive Reasoning}

@@

\section{Cohandlers as Separate Constructs}

@@

\section{Coexamples}

    TODO Introduction into coeffects from Freak side

@@

@@

        <Values V, W> $::=$ $ x $ \\
            | $nat \; n$ | `string'  \\
            | $ \backslash x : A \rightarrow M $ | \textbf{rec} $ g \; x \rightarrow M $\\
            | $V \oplus W$ | $V \approx W$ \\
            | <> | $ \{ \ell = V; W\} $  | ${[ \ell \; V]}^{R}$

        <Computations M, N> $::=$ $ V $ $ W $ \\
            | \textbf{if} $V$ \textbf{then} $M$ \textbf{else} $N$ \\
            | \textbf{let} $\{\ell  = x; y\} = V$ \textbf{in} $ N $ \\
            | \textbf{case} $V \{ \ell \; x \rightarrow M; y \rightarrow N\}$ | \textbf{absurd} $ V $ \\
            | \textbf{return} $V$ | \textbf{let} $ x \leftarrow M $ \textbf{in} $ N $ \\
            | \textbf{do} $\ell \; V$ | \textbf{handle} $M$ \textbf{with} $ \{ H \} $

@@

@@

    \section{Cohandlers}
    \ldots

>>>>

    \subsection{Coinductive Reasoning}\label{subsec:coinduction}

@@

\section{Cohandlers as Separate Constructs}\label{sec:cohandlers-solution}

@@

\section{Coexamples}\label{sec:coexamples}

    We are going to give here informal introduction to programming with
    coeffects in Freak, based on what we have stated in
    Section~\ref{sec:duality} and Section~\ref{sec:cohandlers-solution}.
    Elimination of effects has the following syntax:

\begin{verbatim}
    cohandle <Algebraic Theory> using <Initial state> at
        <computation>
    through <handler>
\end{verbatim}

    Where algebraic theory is a name for signature of coeffects that we
    handle, with initial coalgebra carrier holding \verb!<Initial state>! value.
    Handler is syntactically same as in the case of standard algebraic effects,
    however, the parameter passed to cohandler is always a pair of
    current configuration and actual argument passed by user to effect.

    Introduction rule for coeffects is written as \verb!observe Coeffect p!,
    which references observations from coinduction described in
    Subsection~\ref{subsec:coinduction}.

@@

    Cohandlers are as they were introduced in Section~\ref{sec:coexamples},
    where $AlgTheory$ is an identifier representing our signature.

@@

        <Values V, W> $::=$ $ x $ \\
            | $nat \; n$ | `string'  \\
            | $ \backslash x : A \rightarrow M $ \\
            | \textbf{rec} $ g \; x \rightarrow M $\\
            | $V \oplus W$ | $V \approx W$ \\
            | () | ($V$, $W$) \\
            | \textbf{fst} $V$ | \textbf{snd} $V$

        <Computations M, N> $::=$ $ V $ $ W $ \\
            | \textbf{if} $V$ \textbf{then} $M$ \textbf{else} $N$ \\
            | \textbf{return} $V$ \\
            | \textbf{absurd} $ V $ \\
            | \textbf{let} $ x \leftarrow M $ \textbf{in} $ N $ \\
            | \textbf{do} $\ell \; V$ \\
            | \textbf{handle} $M$ \textbf{with} $ \{ H \} $ \\
            | \textbf{observe} $\ell \; V$ \\
            | \textbf{cohandle} $AlgTheory$ \textbf{using} $V$ \textbf{at} $M$ \textbf{through} $ \{ H \} $

@@

    \subsection{Cohandlers}

@@

    \section{Cohandlers}

    Similarly as in Section~\ref{sec:cohandlers-solution}, we are going to
    divide this into three parts.

    TODO Describe the transformation here.

    TODO it's not implemented yet. Be more clear what's happening here

    Linear usages of resumptions is asserted by analyzing parsed AST tree,
    where in every leaf there must be a return statement. It's value is then
    passed into continuation of a cohandler.

    Guards for not letting effect pass cohandler is implemented in CPS
    translation, more specifically, code that translates cohandler ensures that
    argument passed in resumption is not an effect. This is done on a static
    level before evaluation, which is a desired behaviour.
